---
title: "Copy number variant metrics"
author: Astrid Deschênes and Pascal Belleau
output:
  BiocStyle::html_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{Copy number variant metrics}
  %\VignettePackage{CNVMetrics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r style, echo = FALSE, results = 'asis', warning=FALSE, message=FALSE}
BiocStyle::markdown()
library(knitr)
library(GenomeInfoDb)

```

<br />
**Package**: `r Rpackage("CNVMetrics")`<br />
**Authors**: `r packageDescription("CNVMetrics")[["Author"]]`<br />
**Version**: `r packageDescription("CNVMetrics")$Version`<br />
**Compiled date**: `r Sys.Date()`<br />
**License**: `r packageDescription("CNVMetrics")[["License"]]`<br />


# Licensing 

The `r Githubpkg("adeschen/CNVMetrics")` package and the underlying 
`r Githubpkg("adeschen/CNVMetrics")` code are distributed under the 
Artistic license 2.0. You are free to use and redistribute this software. 

# Introduction



# Inputs

## Chromosomes information 

The chromosomes information is mandatory. It ensures that only the selected
chromoromes are used in the analysis. As not all CNV software use the same
reference (reference with alternive regions or not), it ensure that
all samples will be compared using the same reference. We strongly suggest 
using only the primary chromosomes for this analaysis.

The chromosomes information is contained inside a `Seqinfo` object. The 
information from some UCSC genomes can be fetched automatically using
the `r Biocpkg("GenomeInfoDb")` package. 

```{r knownGenome, collapse=TRUE, eval=FALSE}
### Import needed library
library(GenomeInfoDb)

### Get the information for Human genome version 19
hg19Info <- Seqinfo(genome="hg19")

### Subset the object to keep only the analyzed chromosomes
hg19Subset <- hg19Info[c("chr1", "chr10", "chrX")]
```

A `Seqinfo` object can also be created using the chromosomes information 
specific to the analyzed genome.

```{r newGenome, collapse=FALSE}
### Create an Seqinfo Object
chrInfo <- Seqinfo(seqnames=c("chr1", "chr2", "chr3"),
            seqlengths=c(10000, 20000, 1500), isCircular=c(FALSE, FALSE, FALSE),
            genome="Alien")
```

```{r deleteChr, echo=FALSE, message=FALSE}
if (exists("chrInfo", inherits = FALSE)) rm(chrInfo)
if (exists("hg19Subset", inherits = FALSE)) rm(hg19Subset)
if (exists("hg19Info", inherits = FALSE)) rm(hg19Info)
```


